### 2021-10-13 content/80.formal-definition.tex
More footnotes for lovely PDF world

An $ROCrate(R)$ is defined as a self-described \emph{Root Data Entity}, which describes and contains parts (\emph{data entities}), which are further described in \emph{contextual entities}.  These terms align with their use in the \href{https://www.researchobject.org/ro-crate/1.1/terminology}{RO-Crate 1.1 terminology}.

The $Root(r)$ is a type of $Dataset(r)$, and must have the metadata to literal attributes to provide a $name$, $description$ and $datePublished$, as well as a contextual entity identifying its license. These predicates correspond to the RO-Crate 1.1 \href{https://www.researchobject.org/ro-crate/1.1/root-data-entity.html#direct-properties-of-the-root-data-entity}{requirements for the root data entity}.

The concept of an $Entity(e)$ is introduced as being either a $DataEntity(e)$, a $ContextualEntity(e)$, or \href{https://www.researchobject.org/ro-crate/1.1/contextual-entities.html#contextual-vs-data-entities}{both}; and must be typed with at least one $Class(e)$.

@@

An important RO-Crate principle is that of being \textbf{self-described} Therefore the serialisation of the RO-Crate into a file should also describe itself in a \href{https://www.researchobject.org/ro-crate/1.1/root-data-entity.html#ro-crate-metadata-file-descriptor}{Metadata File Descriptor}, indicating it is $about$ (describing) the RO-Crate root data entity, and that it $conformsTo$ a particular version of the RO-Crate specification:

@@

Combining the above predicates and schema.org mapping with rudimentary JSON templates, these forward-chaining production rules can output JSON-LD according to the RO-Crate 1.1 specification\footnote{
    \textbf{Limitations:} Contextual entities not related from the RO-Crate (e.g. using inverse relations to a data entity) would not be covered by the single direction $Mentions(R, s)$ production rule; see \href{https://github.com/ResearchObject/ro-crate/issues/122}{issue 122}. The $datePublished(e, d)$ rule do not include syntax checks for the ISO 8601 datetime format. Compared with RO-Crate examples, this generated JSON-LD does not use a $@context$ as the IRIs are produced unshortened, a post-step could do JSON-LD Flattening with a versioned RO-Crate context. The \texttt{@type} expansion is included for clarity, even though this is also implied by the $type(e, t)$ expansion to $Relation(e, \texttt{xsd:type})$.
}:

>>>>

An $ROCrate(R)$ is defined as a self-described \emph{Root Data Entity}, which describes and contains parts (\emph{data entities}), which are further described in \emph{contextual entities}.  These terms align with their use in the RO-Crate 1.1 terminology\footnote{
    \url{https://www.researchobject.org/ro-crate/1.1/terminology}}.

The $Root(r)$ is a type of $Dataset(r)$, and must have the metadata to literal attributes to provide a $name$, $description$ and $datePublished$, as well as a contextual entity identifying its license. These predicates correspond to the RO-Crate 1.1 requirements for the root data entity\footnote{
    \href{https://www.researchobject.org/ro-crate/1.1/root-data-entity.html\#direct-properties-of-the-root-data-entity}
}.

The concept of an $Entity(e)$ is introduced as being either a $DataEntity(e)$, a $ContextualEntity(e)$, or both\footnote{
    \href{https://www.researchobject.org/ro-crate/1.1/contextual-entities.html\#contextual-vs-data-entities}
}; and must be typed with at least one $Class(e)$.

@@

An important RO-Crate principle is that of being \textbf{self-described} Therefore the serialisation of the RO-Crate into a file should also describe itself in a Metadata File Descriptor\footnote{
    \url{https://www.researchobject.org/ro-crate/1.1/root-data-entity.html\#ro-crate-metadata-file-descriptor}
}, indicating it is $about$ (describing) the RO-Crate root data entity, and that it $conformsTo$ a particular version of the RO-Crate specification:

@@

Combining the above predicates and schema.org mapping with rudimentary JSON templates, these forward-chaining production rules can output JSON-LD according to the RO-Crate 1.1 specification\footnote{
    \textbf{Limitations:} Contextual entities not related from the RO-Crate (e.g. using inverse relations to a data entity) would not be covered by the single direction $Mentions(R, s)$ production rule; see \href{https://github.com/ResearchObject/ro-crate/issues/122}{GitHub issue ResearchObject/ro-crate\#122}. The $datePublished(e, d)$ rule do not include syntax checks for the ISO 8601 datetime format. Compared with RO-Crate examples, this generated JSON-LD does not use a $@context$ as the IRIs are produced unshortened, a post-step could do JSON-LD Flattening with a versioned RO-Crate context. The \texttt{@type} expansion is included for clarity, even though this is also implied by the $type(e, t)$ expansion to $Relation(e, \texttt{xsd:type})$.
}:
